---
title: "Task 5a"
format: html
editor: visual
execute: 
  warning: false
---

Up here\^\^\^\^\^

```{r}
library(tidyverse)

```

Normally i'd use pacman but in library it shows all the printed output

So lets supress some information JUST FOR THIS CHUNK

```{r}
#| warning: false
#| message: false
library(tidyverse)
```

Thats a lot cleaner

Running code not showing code or output

```{r}
#| include: false #removes all output 
# Return first 6 lines of data
head(starwars)

#Returns dimensions 
dim(starwars)
```

Lets plot that star wars data showing output but not code

```{r}
#| warning: false
#| echo: false
#We only want the graph
ggplot(starwars, aes(height,mass, color=mass))+
  geom_point()+
  labs(x= "Height (cm)", 
       y = "Mass (kg)")+
  theme_linedraw()

```

Now lets make a histogram show only code and output

```{r}
#| warning: false
#| fig-cap: "caption text"
#| fig-alt: "figure alt text"
ggplot(starwars, aes(x = height))+
  geom_histogram(color = "red", fill = "limegreen")

```

So far we've only been putting these in each We can put ts in the HEADER.

find summary stats for star wars characters

```{r}

sw_height_mean <- mean(starwars$height, na.rm = T); sw_height_mean
sw_height_median <- median(starwars$height,
                           na.rm = T)
sw_height_var <- var(starwars$height, na.rm = T)
sw_height_sd <- sd(starwars$height, na.rm = TRUE)
```

Lets try to inline report this

The mean height of the characters in Star Wars is `r round(sw_height_mean, 1)` cm.

The median height of the characters in Star Wars is `r sw_height_median` cm.
